Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2024-03-30 2_SSL_NE/article/article_supplementary.tex
various updates

\begin{figure}[h!]
\centering
\includegraphics[height=15cm]{figures/chip_architecture_overview.pdf}
\caption{\textbf{Historical evolution of LED chip architectures.} Panel A: classical chip with lateral current spreading; Panel B: Osram’s thin GaN flip-chip (vertical) architecture; Panel C: flip-chip architecture; Panel D: chip-scale package flip-chip architecture. Shown are side views of chips without packages, along a cutaway line best suited to the features of each architecture. The cutaway surface is indicated by a red arrow with an eye on the overlaid top view of each chip. Note that the dimensions are not to scale, and smaller features are greatly exaggerated for clarity. Years indicated correspond to the earliest identified patent priority date. Black frames around certain designs indicate chip designs not brought to large-scale production. Additional context on this figure is provided in \cref{sec:subeff_progress}. Chip architecture abbreviations: TF - Thin-Film; FC - Flip-Chip; CSP - Chip-Scale Package; Material abbreviations: GaN - Gallium Nitride, ITO - Indium Tin Oxide, MQW - Multiple Quantum Well. Source: adapted and compiled from multiple patents and industry publications. See Supplementary Note 16 for the full list of sources and references.}
\label{fgr:chip_architecture_overview}
\end{figure}

@@

While generally comprehensive, the model is limited by the availability of performance data for the most recent manufacturing equipment, as well as the confidential nature of cost structures of Asia-based manufacturing lines. A complete treatment of the limitations of the model is provided in \cref{sec:costmodel_structure}.

@@

\subsection{Yielded Cost}
\label{sec:cost_computation}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[height=15cm]{figures/chip_architecture_overview.pdf}
\caption{\textbf{Historical evolution of LED chip architectures.} Panel A: classical chip with lateral current spreading; Panel B: Osram’s thin GaN flip-chip (vertical) architecture; Panel C: flip-chip architecture; Panel D: chip-scale package flip-chip architecture. Shown are side views of chips without packages, along a cutaway line best suited to the features of each architecture. The cutaway surface is indicated by a red arrow with an eye on the overlaid top view of each chip. Note that the dimensions are not to scale, and smaller features are greatly exaggerated for clarity. Years indicated correspond to the earliest identified patent priority date. Dashed black frames around certain designs indicate chip designs not brought to large-scale production. Additional context on this figure is provided in \cref{sec:subeff_progress}. Chip architecture abbreviations: TF - Thin-Film; FC - Flip-Chip; CSP - Chip-Scale Package; Material abbreviations: GaN - Gallium Nitride, ITO - Indium Tin Oxide, MQW - Multiple Quantum Well. Source: adapted and compiled from multiple patents and industry publications. See Supplementary Note 16 for the full list of sources and references.}
\label{fgr:chip_architecture_overview}
\end{figure}

@@

@@

Unfortunately, benchmarking the total cost computed with our model against industry data is not possible. While the US Department of Energy has managed to convince companies to share their cost structure (shown in Supplementary Figure 16), they never share \textit{absolute} cost. The closest industry publication ever comes to disclosing absolute cost data is in their reporting data on \$/klm at the chip-level. Our model (like most other manufacturing cost models we reviewed) computes only the total manufacturing cost, since a combined computation of cost and performance would require a highly complex treatment not only of the cost associated with equipment performance, but also of the associated changes in the bulk semiconductor, phosphor, packaging, etc. To the best of our knowledge, this has not been attempted, at least in a publicly available fashion, for solid-state lighting devices.

\clearpage
\subsection{Yielded Cost}
\label{sec:cost_computation}
